---
title: "Veersemeer"
author: "Willem Stolte"
date: "Friday, May 22, 2015"
output: ioslides_presentation
runtime: shiny
---
```{r load_packages, include=FALSE}
library(ggplot2)
library(plyr)
library(pander)
```

## Shiny Presentation

This R Markdown presentation is made interactive using Shiny. The viewers of the presentation can change the assumptions underlying what's presented and see the results immediately. 

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Waar is allemaal gemonsterd?

```{r, echo=F}
load(file = "R/DATA/MWTL_Veersemeer_bewerkt.Rdata")
print(ddply(rws_dat, .(locatie), summarize, startjaar = format(min(datetime), format = "%Y"), eindjaar = format(max(datetime), format = "%Y")), row.names = F)
```

## Slide with Interactive Plot

```{r, echo=FALSE}
inputPanel(selectInput("location", "Location:", selected = "Soelekerkepolder oost", 
                       choices = levels(rws_dat$locatie)),
           selectInput("substance", "Substance:", selected = "saliniteit", 
                       choices = levels(as.factor(rws_dat$variable))),
           sliderInput("lspan", "Loess span", value = 0.3,
                       min = 0, max = 1, 0.7, step = 0.05, sep = "")
           )
renderPlot({width = 0.5
            subdf = subset(rws_dat, rws_dat$variable == input$substance &
                             rws_dat$locatie == input$location)
            require(ggplot2)
            pl <- ggplot(subdf, aes(datetime, waarde))
            pl + 
              geom_point(aes(), color = "seagreen4", alpha = 0.5) + 
              geom_smooth(aes(), method='loess', span = input$lspan, size = 1) +
              theme_classic(base_size = 18)
            })
```

## Wat is er eigenlijk gebeurd?

1) Overgang van zoet naar zout water.... blabla
2) Nutrienten in overgangsperiode blabla
3) Zuurstof ..... 

## Conclusies


